Mechanising Recursion Schemes with Magic-Free Coq Extraction

### 2024-03-18 paper/paper.tex
Stuff

>>>>

\section{Conclusions and Future Work}

Hylomorphisms are a general recursion scheme that can encode any other 
recursion scheme, and that satisfy a number of algebraic laws that can be used
to reason about program equivalences. Despite their useful properties, not many 
pieces of work formalise them in a proof assistant, partly due to the difficulty
of dealing with termination, and reasoning about program equivalences. In this work,
we tackle these problems by
